---
title: "MIMC-data-descriptives"
author: "HazelAvdW"
date: "03-12-2025"
output: html_document
---

# Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r libraries, echo=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
library(stringr)
```

# Load Data
```{r load data, echo=FALSE}
setwd('/Users/hazelaileenvanderwalle/Library/CloudStorage/OneDrive-Personal/work/study/PhD/_PROJECT/_MIMC_QDA/BBB_QDA/data checking')
ds <- read.csv('MIMCdata.csv')

cat("Dataset loaded successfully\n")
cat("Total observations:", nrow(ds), "\n")
cat("Total columns:", ncol(ds), "\n")
```

# Participant-Grouped Data
```{r participant grouped dataframe, echo=FALSE}
# Group data by Prolific ID
ds_ptpGrouped <- ds %>%
  group_by(PROLIFIC_PID) %>%
  summarise(
    Participant_ID = first(participant_ID),
    PROLIFIC_PID = first(PROLIFIC_PID),
    File_ID = first(File_ID),
    Headphones = first(demographics.headphones),
    Gender = first(demographics.gender),
    Stimulus_Group = first(stimulus_group),
    expName = first(expName),
    Age = first(demographics.age),
    Age_Group = first(age_group),
    Country_Code = first(country_code),
    Living_Country = first(demographics.livingCountry),
    Birth_Country = first(demographics.birthCountry),
    Native_Language = first(demographics.nativeLanguage),
    Other_Language = first(demographics.otherLanguage),
    Other_Language_Text = first(demographics.otherLanguageText),
    Education_Level = first(demographics.education),
    Musician_Identification = first(demographics.musicianIdentification),
    Hearing_Impairments = first(demographics.hearingImpariments),
    Hearing_Impairments_Text = first(demographics.hearingImpairmentsText),
    Date = first(date),
    Feedback = first(demographics.feedback)
  ) %>%
  ungroup()

cat("Total unique participants:", nrow(ds_ptpGrouped), "\n")
```

# Basic Descriptive Statistics

## Age Statistics
```{r age statistics, echo=FALSE}
cat("~~~ AGE STATISTICS ~~~\n\n")
cat("Mean age:", round(mean(ds_ptpGrouped$Age, na.rm = TRUE), 2), "\n")
cat("Median age:", median(ds_ptpGrouped$Age, na.rm = TRUE), "\n")
cat("SD age:", round(sd(ds_ptpGrouped$Age, na.rm = TRUE), 2), "\n")
cat("Min age:", min(ds_ptpGrouped$Age, na.rm = TRUE), "\n")
cat("Max age:", max(ds_ptpGrouped$Age, na.rm = TRUE), "\n")
cat("Age NA count:", sum(is.na(ds_ptpGrouped$Age)), "\n")
```

## Categorical Demographics
```{r categorical demographics, echo=FALSE}
# Function to summarise categorical variables
sum_cat <- function(data, column_name) {
  cat(sprintf("\n~~~ %s ~~~\n", toupper(column_name)))
  counts <- table(data[[column_name]], useNA = "ifany")
  
  for (value in names(counts)) {
    percentage <- round(counts[value] / sum(counts) * 100, 1)
    cat(sprintf("%s: %d (%.1f%%)\n", value, counts[value], percentage))
  }
}

# Demographics summaries
sum_cat(ds_ptpGrouped, "Gender")
sum_cat(ds_ptpGrouped, "Age_Group")
sum_cat(ds_ptpGrouped, "Country_Code")
sum_cat(ds_ptpGrouped, "Living_Country")
sum_cat(ds_ptpGrouped, "Birth_Country")
sum_cat(ds_ptpGrouped, "Native_Language")
sum_cat(ds_ptpGrouped, "Headphones")
sum_cat(ds_ptpGrouped, "Education_Level")
sum_cat(ds_ptpGrouped, "Musician_Identification")
sum_cat(ds_ptpGrouped, "Hearing_Impairments")
sum_cat(ds_ptpGrouped, "Hearing_Impairments_Text")
sum_cat(ds_ptpGrouped, "Stimulus_Group")
sum_cat(ds_ptpGrouped, "expName")
```

# MIMC Analysis

## Overall MIMC Frequency
```{r overall MIMC frequency, echo=FALSE}
cat("\n~~~ OVERALL MIMC FREQUENCY ~~~\n\n")

na_strings <- c("NA", "N/A", "na", "n/a", "Na", "N/a")

# Identify MIMC responses and clean free-text columns
ds_MIMC <- ds %>%
  mutate(
    thought_or_not_response.keys = trimws(thought_or_not_response.keys),
    have_thought_input.text = ifelse(trimws(have_thought_input.text) %in% na_strings, NA, have_thought_input.text),
    no_thought_input.text   = ifelse(trimws(no_thought_input.text)   %in% na_strings, NA, no_thought_input.text),
    # Only count as MIMC if button = 'y' AND thought text box is not NA
    is_MIMC    = ifelse(thought_or_not_response.keys == 'y' & !is.na(have_thought_input.text), 1, 0),
    # Only count as no-MIMC if button = 'n' AND no-thought text box is not NA
    is_no_MIMC = ifelse(thought_or_not_response.keys == 'n' & !is.na(no_thought_input.text), 1, 0)
  )

total_MIMCs    <- sum(ds_MIMC$is_MIMC, na.rm = TRUE)
total_no_MIMCs <- sum(ds_MIMC$is_no_MIMC, na.rm = TRUE)
valid_trials  <- total_MIMCs + total_no_MIMCs
MIMC_rate      <- round(total_MIMCs / valid_trials * 100, 2)

cat("Total valid trials:", valid_trials, "\n")
cat("Total MIMCs (thought reports):", total_MIMCs, "\n")
cat("Total no-MIMCs:", total_no_MIMCs, "\n")
cat("Overall MIMC rate:", MIMC_rate, "%\n")
cat("Trials with missing/invalid response:", nrow(ds_MIMC) - valid_trials, "\n")

# Thought report word count stats
thought_reports <- ds_MIMC %>%
  filter(is_MIMC == 1) %>%
  mutate(word_count = sapply(strsplit(trimws(have_thought_input.text), "\\s+"), length))

if (nrow(thought_reports) > 0) {
  cat("\nThought report word count:\n")
  cat("  Mean:  ", round(mean(thought_reports$word_count),   2), "\n")
  cat("  Median:", round(median(thought_reports$word_count), 2), "\n")
  cat("  SD:    ", round(sd(thought_reports$word_count),     2), "\n")
  cat("  Min:   ", min(thought_reports$word_count),              "\n")
  cat("  Max:   ", max(thought_reports$word_count),              "\n")
} else {
  cat("\nNo thought reports with text found.\n")
}
```

## (optional run) No thought reason
uncomment out the below code to read the no-MIMC responses (fair warning: it's long)
```{r no MIMC response, echo=FALSE}
#cat("\n~~~ REPORTED NO THOUGHT REASONS ~~~\n\n")
#sum_cat(ds, "no_thought_input.text")
```


## MIMCs by Participant
```{r MIMCs by participant, echo=FALSE}
cat("\n~~~ MIMC FREQUENCY BY PARTICIPANT ~~~\n\n")

MIMC_by_participant <- ds_MIMC %>%
  group_by(participant_ID, PROLIFIC_PID) %>%
  summarise(
    total_trials = n(),
    MIMCs = sum(is_MIMC, na.rm = TRUE),
    no_MIMCs = sum(is_no_MIMC, na.rm = TRUE),
    MIMC_rate = round(MIMCs / total_trials * 100, 1),
    .groups = 'drop'
  )

cat("Mean MIMCs per participant:", round(mean(MIMC_by_participant$MIMCs), 2), "\n")
cat("SD MIMCs per participant:", round(sd(MIMC_by_participant$MIMCs), 2), "\n")
cat("Median MIMCs per participant:", median(MIMC_by_participant$MIMCs), "\n")
cat("Min MIMCs per participant:", min(MIMC_by_participant$MIMCs), "\n")
cat("Max MIMCs per participant:", max(MIMC_by_participant$MIMCs), "\n")

cat("\nMIMC rate distribution:\n")
summary(MIMC_by_participant$MIMC_rate)

# Histogram of MIMC rates
hist(MIMC_by_participant$MIMC_rate, 
     breaks = 20,
     main = "Distribution of MIMC Rates Across Participants",
     xlab = "MIMC Rate (%)",
     ylab = "Number of Participants",
     col = "skyblue")
```

## MIMCs by Genre
```{r MIMCs by genre, echo=FALSE}
cat("\n~~~ MIMC FREQUENCY BY GENRE ~~~\n\n")

MIMC_by_genre <- ds_MIMC %>%
  group_by(genre_code) %>%
  summarise(
    total_trials = n(),
    MIMCs = sum(is_MIMC, na.rm = TRUE),
    no_MIMCs = sum(is_no_MIMC, na.rm = TRUE),
    MIMC_rate = round(MIMCs / total_trials * 100, 1),
    .groups = 'drop'
  ) %>%
  arrange(desc(MIMC_rate))

print(MIMC_by_genre)

# Bar plot
ggplot(MIMC_by_genre, aes(x = reorder(genre_code, MIMC_rate), y = MIMC_rate)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(title = "MIMC Rate by Genre",
       x = "Genre",
       y = "MIMC Rate (%)") +
  theme_minimal()


# Overall chi-square
genre_matrix <- MIMC_by_genre %>% select(MIMCs, no_MIMCs) %>% as.matrix()
rownames(genre_matrix) <- MIMC_by_genre$genre_code
genre_chi <- chisq.test(genre_matrix)
# Cramer's V effect size
n_total <- sum(genre_matrix)
cramer_v <- sqrt(genre_chi$statistic / (n_total * (min(nrow(genre_matrix), ncol(genre_matrix)) - 1)))
#Cramér's V is the standard effect size for chi-square — small ≈ .10, medium ≈ .30, large ≈ .50.
cat("\nOverall chi-square test across genres:\n")
cat(sprintf("  χ²(%d, N = %d) = %.2f, p %s, V = %.3f\n",
    genre_chi$parameter,
    n_total,
    genre_chi$statistic,
    ifelse(genre_chi$p.value < .001, "< .001", paste0("= ", round(genre_chi$p.value, 3))),
    cramer_v))

# Pairwise chi-square with Bonferroni correction
cat("\nPairwise chi-square tests (Bonferroni corrected):\n")
genres <- MIMC_by_genre$genre_code
n_genres <- length(genres)
pairwise_results <- data.frame()

for (i in 1:(n_genres - 1)) {
  for (j in (i + 1):n_genres) {
    pair_matrix <- genre_matrix[c(genres[i], genres[j]), ]
    pair_chi <- chisq.test(pair_matrix)
    pairwise_results <- rbind(pairwise_results, data.frame(
      Group1 = genres[i],
      Group2 = genres[j],
      X2     = round(pair_chi$statistic, 3),
      df     = pair_chi$parameter,
      p_raw  = pair_chi$p.value
    ))
  }
}

pairwise_results$p_bonferroni <- p.adjust(pairwise_results$p_raw, method = "bonferroni")
pairwise_results$p_raw        <- format.pval(pairwise_results$p_raw, digits = 3, eps = .001)
pairwise_results$p_bonferroni <- format.pval(pairwise_results$p_bonferroni, digits = 3, eps = .001)
print(pairwise_results, row.names = FALSE)

```

## MIMCs by Country
```{r MIMCs by country, echo=FALSE}
cat("\n~~~ MIMC FREQUENCY BY COUNTRY ~~~\n\n")

MIMC_by_country <- ds_MIMC %>%
  group_by(country_code) %>%
  summarise(
    total_trials = n(),
    participants = n_distinct(participant_ID),
    MIMCs = sum(is_MIMC, na.rm = TRUE),
    no_MIMCs = sum(is_no_MIMC, na.rm = TRUE),
    MIMC_rate = round(MIMCs / total_trials * 100, 1),
    .groups = 'drop'
  ) %>%
  arrange(desc(MIMC_rate))

print(MIMC_by_country)

# Bar plot
ggplot(MIMC_by_country, aes(x = country_code, y = MIMC_rate)) +
  geom_bar(stat = "identity", fill = "coral") +
  labs(title = "MIMC Rate by Country",
       x = "Country",
       y = "MIMC Rate (%)") +
  theme_minimal()


# Chi-square test across countries
country_matrix <- MIMC_by_country %>%
  select(MIMCs, no_MIMCs) %>%
  as.matrix()
rownames(country_matrix) <- MIMC_by_country$country_code
country_chi <- chisq.test(country_matrix)
#
n_total_country <- sum(country_matrix)
cramer_v_country <- sqrt(country_chi$statistic / (n_total_country * (min(nrow(country_matrix), ncol(country_matrix)) - 1)))
#Note that for this country comparison (2×2 table), Cramér's V is equivalent to the phi coefficient, which is the conventional effect size for 2×2 chi-squares.
cat("\nChi-square test (UK vs US — only one pair so no correction needed):\n")
cat(sprintf("  χ²(%d, N = %d) = %.2f, p %s, V = %.3f\n",
    country_chi$parameter,
    n_total_country,
    country_chi$statistic,
    ifelse(country_chi$p.value < .001, "< .001", paste0("= ", round(country_chi$p.value, 3))),
    cramer_v_country))

```

## MIMCs by Age Group
```{r MIMCs by age group, echo=FALSE}
cat("\n~~~ MIMC FREQUENCY BY AGE GROUP ~~~\n\n")

MIMC_by_age <- ds_MIMC %>%
  group_by(age_group) %>%
  summarise(
    total_trials = n(),
    participants = n_distinct(participant_ID),
    MIMCs = sum(is_MIMC, na.rm = TRUE),
    no_MIMCs = sum(is_no_MIMC, na.rm = TRUE),
    MIMC_rate = round(MIMCs / total_trials * 100, 1),
    .groups = 'drop'
  ) %>%
  arrange(age_group)

print(MIMC_by_age)

# Bar plot
ggplot(MIMC_by_age, aes(x = age_group, y = MIMC_rate)) +
  geom_bar(stat = "identity", fill = "seagreen") +
  labs(title = "MIMC Rate by Age Group",
       x = "Age Group",
       y = "MIMC Rate (%)") +
  theme_minimal()


# Overall chi-square
age_matrix <- MIMC_by_age %>% select(MIMCs, no_MIMCs) %>% as.matrix()
rownames(age_matrix) <- MIMC_by_age$age_group
age_chi <- chisq.test(age_matrix)
n_total_age <- sum(age_matrix)
cramer_v_age <- sqrt(age_chi$statistic / (n_total_age * (min(nrow(age_matrix), ncol(age_matrix)) - 1)))
#
cat("\nOverall chi-square test across age groups:\n")
cat(sprintf("  χ²(%d, N = %d) = %.2f, p %s, V = %.3f\n",
    age_chi$parameter,
    n_total_age,
    age_chi$statistic,
    ifelse(age_chi$p.value < .001, "< .001", paste0("= ", round(age_chi$p.value, 3))),
    cramer_v_age))

# Pairwise chi-square with Bonferroni correction
cat("\nPairwise chi-square tests (Bonferroni corrected):\n")
age_groups <- MIMC_by_age$age_group
n_ages <- length(age_groups)
pairwise_age <- data.frame()

for (i in 1:(n_ages - 1)) {
  for (j in (i + 1):n_ages) {
    pair_matrix <- age_matrix[c(as.character(age_groups[i]), as.character(age_groups[j])), ]
    pair_chi <- chisq.test(pair_matrix)
    pairwise_age <- rbind(pairwise_age, data.frame(
      Group1 = age_groups[i],
      Group2 = age_groups[j],
      X2     = round(pair_chi$statistic, 3),
      df     = pair_chi$parameter,
      p_raw  = pair_chi$p.value
    ))
  }
}

pairwise_age$p_bonferroni <- p.adjust(pairwise_age$p_raw, method = "bonferroni")
pairwise_age$p_raw        <- format.pval(pairwise_age$p_raw, digits = 3, eps = .001)
pairwise_age$p_bonferroni <- format.pval(pairwise_age$p_bonferroni, digits = 3, eps = .001)
print(pairwise_age, row.names = FALSE)
```

## MIMCs by Clip
```{r MIMCs by clip, echo=FALSE}
cat("\n~~~ MIMC FREQUENCY BY CLIP ~~~\n\n")

MIMC_by_clip <- ds_MIMC %>%
  group_by(full_clip_name, clip_label, genre_code) %>%
  summarise(
    total_trials = n(),
    MIMCs = sum(is_MIMC, na.rm = TRUE),
    no_MIMCs = sum(is_no_MIMC, na.rm = TRUE),
    MIMC_rate = round(MIMCs / total_trials * 100, 1),
    .groups = 'drop'
  ) %>%
  arrange(desc(MIMC_rate))

print(MIMC_by_clip)

cat("\nTop 10 clips with highest MIMC rates:\n")
print(head(MIMC_by_clip, 10))

cat("\nBottom 10 clips with lowest MIMC rates:\n")
print(tail(MIMC_by_clip, 10))

# Summary statistics
cat("\nMIMC rate across clips:\n")
summary(MIMC_by_clip$MIMC_rate)
```

## Cross-Tabulations

### MIMCs by Genre x Country
```{r MIMCs genre x country, echo=FALSE}
cat("\n~~~ MIMC FREQUENCY BY GENRE x COUNTRY ~~~\n\n")

MIMC_genre_country <- ds_MIMC %>%
  group_by(genre_code, country_code) %>%
  summarise(
    total_trials = n(),
    MIMCs = sum(is_MIMC, na.rm = TRUE),
    MIMC_rate = round(MIMCs / total_trials * 100, 1),
    .groups = 'drop'
  ) %>%
  pivot_wider(names_from = country_code, 
              values_from = c(total_trials, MIMCs, MIMC_rate),
              names_sep = "_")

print(MIMC_genre_country)
```

### MIMCs by Genre x Age Group
```{r MIMCs genre x age, echo=FALSE}
cat("\n~~~ MIMC FREQUENCY BY GENRE x AGE GROUP ~~~\n\n")

MIMC_genre_age <- ds_MIMC %>%
  group_by(genre_code, age_group) %>%
  summarise(
    total_trials = n(),
    MIMCs = sum(is_MIMC, na.rm = TRUE),
    MIMC_rate = round(MIMCs / total_trials * 100, 1),
    .groups = 'drop'
  ) %>%
  arrange(genre_code, age_group)

# Show as wide format
MIMC_genre_age_wide <- MIMC_genre_age %>%
  select(genre_code, age_group, MIMC_rate) %>%
  pivot_wider(names_from = age_group, values_from = MIMC_rate)

print(MIMC_genre_age_wide)

# Heatmap
ggplot(MIMC_genre_age, aes(x = age_group, y = genre_code, fill = MIMC_rate)) +
  geom_tile() +
  geom_text(aes(label = paste0(MIMC_rate, "%")), color = "white") +
  scale_fill_gradient(low = "lightblue", high = "darkblue") +
  labs(title = "MIMC Rate by Genre and Age Group",
       x = "Age Group",
       y = "Genre",
       fill = "MIMC Rate (%)") +
  theme_minimal()
```

### MIMCs by Country x Age Group
```{r MIMCs country x age, echo=FALSE}
cat("\n~~~ MIMC FREQUENCY BY COUNTRY x AGE GROUP ~~~\n\n")

MIMC_country_age <- ds_MIMC %>%
  group_by(country_code, age_group) %>%
  summarise(
    total_trials = n(),
    MIMCs = sum(is_MIMC, na.rm = TRUE),
    MIMC_rate = round(MIMCs / total_trials * 100, 1),
    .groups = 'drop'
  ) %>%
  arrange(country_code, age_group)

# Show as wide format
MIMC_country_age_wide <- MIMC_country_age %>%
  select(country_code, age_group, MIMC_rate) %>%
  pivot_wider(names_from = age_group, values_from = MIMC_rate)

print(MIMC_country_age_wide)
```

# MIMC Ratings Analysis

## Overall MIMC Ratings
```{r MIMC ratings overall, echo=FALSE}
cat("\n~~~ OVERALL MIMC RATING CHARACTERISTICS ~~~\n\n")

MIMC_ratings_data <- ds_MIMC %>%
  filter(is_MIMC == 1) %>%
  mutate(
    Q1_music_related = as.numeric(rating_Q1_music_related.response),
    Q2_spontaneous = as.numeric(rating_Q2_spontaneous.response),
    Q3_unreality = as.numeric(rating_Q3_reality.response)
  )

cat("Q1: Music-related rating\n")
cat("  To what degree do you think these thoughts were prompted by the music you just heard?\n")
cat("      not at all prompted by the music  1 / 2 / 3 / 4 / 5  entirely prompted by the music\n")
cat("Mean:", round(mean(MIMC_ratings_data$Q1_music_related, na.rm = TRUE), 2), "\n")
cat("SD:", round(sd(MIMC_ratings_data$Q1_music_related, na.rm = TRUE), 2), "\n")
cat("Median:", median(MIMC_ratings_data$Q1_music_related, na.rm = TRUE), "\n")
cat("Range:", min(MIMC_ratings_data$Q1_music_related, na.rm = TRUE), "-", 
    max(MIMC_ratings_data$Q1_music_related, na.rm = TRUE), "\n\n")

cat("Q2: Spontaneous rating\n")
cat("  Please rate the degree to which you deliberately brought these thoughts to mind\n")
cat("  versus they came to mind spontaneously.\n")
cat("      entirely deliberately  1 / 2 / 3 / 4 / 5  entirely spontaneously\n")
cat("Mean:", round(mean(MIMC_ratings_data$Q2_spontaneous, na.rm = TRUE), 2), "\n")
cat("SD:", round(sd(MIMC_ratings_data$Q2_spontaneous, na.rm = TRUE), 2), "\n")
cat("Median:", median(MIMC_ratings_data$Q2_spontaneous, na.rm = TRUE), "\n")
cat("Range:", min(MIMC_ratings_data$Q2_spontaneous, na.rm = TRUE), "-", 
    max(MIMC_ratings_data$Q2_spontaneous, na.rm = TRUE), "\n\n")

cat("Q3: Unreality rating\n")
cat("  To what degree were these thoughts memories of things you’ve seen or experienced before,\n")
cat("  versus things you’ve newly imagined?\n")
cat("      not at all prompted by the music  1 / 2 / 3 / 4 / 5  entirely prompted by the music\n")
cat("Mean:", round(mean(MIMC_ratings_data$Q3_unreality, na.rm = TRUE), 2), "\n")
cat("SD:", round(sd(MIMC_ratings_data$Q3_unreality, na.rm = TRUE), 2), "\n")
cat("Median:", median(MIMC_ratings_data$Q3_unreality, na.rm = TRUE), "\n")
cat("Range:", min(MIMC_ratings_data$Q3_unreality, na.rm = TRUE), "-", 
    max(MIMC_ratings_data$Q3_unreality, na.rm = TRUE), "\n")
```

## MIMC Ratings by Genre
```{r MIMC ratings by genre, echo=FALSE}
cat("\n~~~ MIMC RATINGS BY GENRE ~~~\n\n")

ratings_by_genre <- MIMC_ratings_data %>%
  group_by(genre_code) %>%
  summarise(
    n_MIMCs = n(),
    Q1_mean = round(mean(Q1_music_related, na.rm = TRUE), 2),
    Q1_sd = round(sd(Q1_music_related, na.rm = TRUE), 2),
    Q2_mean = round(mean(Q2_spontaneous, na.rm = TRUE), 2),
    Q2_sd = round(sd(Q2_spontaneous, na.rm = TRUE), 2),
    Q3_mean = round(mean(Q3_unreality, na.rm = TRUE), 2),
    Q3_sd = round(sd(Q3_unreality, na.rm = TRUE), 2),
    .groups = 'drop'
  ) %>%
  arrange(desc(Q1_mean))

print(ratings_by_genre)

# Visualizations
par(mfrow = c(1, 3))
barplot(ratings_by_genre$Q1_mean, names.arg = ratings_by_genre$genre_code,
        main = "Q1: Music-related by Genre", ylab = "Mean Rating",
        las = 2, col = "steelblue")
barplot(ratings_by_genre$Q2_mean, names.arg = ratings_by_genre$genre_code,
        main = "Q2: Spontaneous by Genre", ylab = "Mean Rating",
        las = 2, col = "coral")
barplot(ratings_by_genre$Q3_mean, names.arg = ratings_by_genre$genre_code,
        main = "Q3: Unreality by Genre", ylab = "Mean Rating",
        las = 2, col = "seagreen")
par(mfrow = c(1, 1))
```

## MIMC Ratings by Country
```{r MIMC ratings by country, echo=FALSE}
cat("\n~~~ MIMC RATINGS BY COUNTRY ~~~\n\n")

ratings_by_country <- MIMC_ratings_data %>%
  group_by(country_code) %>%
  summarise(
    n_MIMCs = n(),
    Q1_mean = round(mean(Q1_music_related, na.rm = TRUE), 2),
    Q1_sd = round(sd(Q1_music_related, na.rm = TRUE), 2),
    Q2_mean = round(mean(Q2_spontaneous, na.rm = TRUE), 2),
    Q2_sd = round(sd(Q2_spontaneous, na.rm = TRUE), 2),
    Q3_mean = round(mean(Q3_unreality, na.rm = TRUE), 2),
    Q3_sd = round(sd(Q3_unreality, na.rm = TRUE), 2),
    .groups = 'drop'
  ) %>%
  arrange(country_code)

print(ratings_by_country)
```

## MIMC Ratings by Age Group
```{r MIMC ratings by age, echo=FALSE}
cat("\n~~~ MIMC RATINGS BY AGE GROUP ~~~\n\n")

ratings_by_age <- MIMC_ratings_data %>%
  group_by(age_group) %>%
  summarise(
    n_MIMCs = n(),
    Q1_mean = round(mean(Q1_music_related, na.rm = TRUE), 2),
    Q1_sd = round(sd(Q1_music_related, na.rm = TRUE), 2),
    Q2_mean = round(mean(Q2_spontaneous, na.rm = TRUE), 2),
    Q2_sd = round(sd(Q2_spontaneous, na.rm = TRUE), 2),
    Q3_mean = round(mean(Q3_unreality, na.rm = TRUE), 2),
    Q3_sd = round(sd(Q3_unreality, na.rm = TRUE), 2),
    .groups = 'drop'
  ) %>%
  arrange(age_group)

print(ratings_by_age)

# Line plots to show age trends
plot_data <- ratings_by_age %>%
  select(age_group, Q1_mean, Q2_mean, Q3_mean) %>%
  pivot_longer(cols = c(Q1_mean, Q2_mean, Q3_mean),
               names_to = "Rating_Type",
               values_to = "Mean_Rating")

ggplot(plot_data, aes(x = age_group, y = Mean_Rating, 
                      color = Rating_Type, group = Rating_Type)) +
  geom_line(linewidth = 1) +
  geom_point(size = 3) +
  scale_color_manual(values = c("Q1_mean" = "steelblue", 
                                 "Q2_mean" = "coral", 
                                 "Q3_mean" = "seagreen"),
                     labels = c("Q1: Music-related", 
                                "Q2: Spontaneous", 
                                "Q3: Unreality")) +
  labs(title = "MIMC Ratings Across Age Groups",
       x = "Age Group",
       y = "Mean Rating",
       color = "Rating Type") +
  theme_minimal() +
  theme(legend.position = "bottom")
```

## MIMC Ratings by Clip
```{r MIMC ratings by clip, echo=FALSE}
cat("\n~~~ MIMC RATINGS BY CLIP ~~~\n\n")

# Check for clip identifier
clip_cols <- c("full_clip_name", "clip_label")
available_clip_cols <- clip_cols[clip_cols %in% colnames(MIMC_ratings_data)]

if(length(available_clip_cols) > 0) {
  clip_id_col <- available_clip_cols[1]
  cat("Using clip identifier:", clip_id_col, "\n\n")
  
  # Check if genre exists
  has_genre <- "genre_code" %in% colnames(MIMC_ratings_data)
  
  if(has_genre) {
    ratings_by_clip <- MIMC_ratings_data %>%
      group_by(across(all_of(c(clip_id_col, "genre_code")))) %>%
      summarise(
        n_MIMCs = n(),
        Q1_mean = round(mean(Q1_music_related, na.rm = TRUE), 2),
        Q1_sd = round(sd(Q1_music_related, na.rm = TRUE), 2),
        Q2_mean = round(mean(Q2_spontaneous, na.rm = TRUE), 2),
        Q2_sd = round(sd(Q2_spontaneous, na.rm = TRUE), 2),
        Q3_mean = round(mean(Q3_unreality, na.rm = TRUE), 2),
        Q3_sd = round(sd(Q3_unreality, na.rm = TRUE), 2),
        .groups = 'drop'
      ) %>%
      arrange(desc(Q1_mean))
  } else {
    ratings_by_clip <- MIMC_ratings_data %>%
      group_by(across(all_of(clip_id_col))) %>%
      summarise(
        n_MIMCs = n(),
        Q1_mean = round(mean(Q1_music_related, na.rm = TRUE), 2),
        Q1_sd = round(sd(Q1_music_related, na.rm = TRUE), 2),
        Q2_mean = round(mean(Q2_spontaneous, na.rm = TRUE), 2),
        Q2_sd = round(sd(Q2_spontaneous, na.rm = TRUE), 2),
        Q3_mean = round(mean(Q3_unreality, na.rm = TRUE), 2),
        Q3_sd = round(sd(Q3_unreality, na.rm = TRUE), 2),
        .groups = 'drop'
      ) %>%
      arrange(desc(Q1_mean))
  }
  
  cat("Total clips with MIMC ratings:", nrow(ratings_by_clip), "\n\n")
  
  cat("Top 10 clips by Q1 (Music-related) rating:\n")
  print(head(ratings_by_clip %>% arrange(desc(Q1_mean)), 10))
  
  cat("\nTop 10 clips by Q2 (Spontaneous) rating:\n")
  print(head(ratings_by_clip %>% arrange(desc(Q2_mean)), 10))
  
  cat("\nTop 10 clips by Q3 (Unreality) rating:\n")
  print(head(ratings_by_clip %>% arrange(desc(Q3_mean)), 10))
  
  # Summary statistics across clips
  cat("\n~~~ RATING VARIABILITY ACROSS CLIPS ~~~\n")
  cat("\nQ1 (Music-related) across clips:\n")
  cat("Mean of clip means:", round(mean(ratings_by_clip$Q1_mean, na.rm = TRUE), 2), "\n")
  cat("SD of clip means:", round(sd(ratings_by_clip$Q1_mean, na.rm = TRUE), 2), "\n")
  cat("Range:", min(ratings_by_clip$Q1_mean, na.rm = TRUE), "-", 
      max(ratings_by_clip$Q1_mean, na.rm = TRUE), "\n\n")
  
  cat("Q2 (Spontaneous) across clips:\n")
  cat("Mean of clip means:", round(mean(ratings_by_clip$Q2_mean, na.rm = TRUE), 2), "\n")
  cat("SD of clip means:", round(sd(ratings_by_clip$Q2_mean, na.rm = TRUE), 2), "\n")
  cat("Range:", min(ratings_by_clip$Q2_mean, na.rm = TRUE), "-", 
      max(ratings_by_clip$Q2_mean, na.rm = TRUE), "\n\n")
  
  cat("Q3 (Unreality) across clips:\n")
  cat("Mean of clip means:", round(mean(ratings_by_clip$Q3_mean, na.rm = TRUE), 2), "\n")
  cat("SD of clip means:", round(sd(ratings_by_clip$Q3_mean, na.rm = TRUE), 2), "\n")
  cat("Range:", min(ratings_by_clip$Q3_mean, na.rm = TRUE), "-", 
      max(ratings_by_clip$Q3_mean, na.rm = TRUE), "\n")
  
} else {
  cat("ERROR: No clip identifier column found!\n")
}
```

# Session Info
```{r session info, echo=FALSE}
sessionInfo()
```